wgcna

### 2019-08-23 analysis/08_wgcna.Rmd
now with 1 function

@@

```{r wgcna, message=FALSE, warning=FALSE, cache=TRUE}
source("08_WGCNA_1.R")

@@

## hypothalas

```{r wgcna-hyp, message=FALSE, warning=FALSE, cache=TRUE}
source("08_WGCNA_1_params.R")
subsetWGCNA("hypothalamus")

@@

```{r wgcna-pit, message=FALSE, warning=FALSE, cache=TRUE}

subsetWGCNA("pituitary")
```

@@

```{r wgcna-gon, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA("gonad")
```

>>>>

source("08_WGCNA_1.R")
```

@@

```{r wgcna, message=FALSE, warning=FALSE, cache=TRUE}

subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary",
                           "male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Characterization dendrogram with trait heatmap")

@@

## Females

```{r wgcna-female, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary"),
            mytitle = "Female sample dendrogram with trait heatmap")

## Males

```{r wgcna-male, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Male sample dendrogram with trait heatmap")

## hypothalamus

```{r wgcna-hyp, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("male.hypothalamus", "female.hypothalamus"),
            mytitle = "Hypothalamus dendrogram with trait heatmap")

@@

```{r wgcna-pit, message=FALSE, warning=FALSE, cache=TRUE}
#subsetWGCNA(c("female.pitutary", "male.pitutary"),
#            mytitle = "Pituitary dendrogram with trait heatmap")
```

@@

```{r wgcna-gon, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("female.gonad", "male.gonad"),
            mytitle = "Gonad dendrogram with trait heatmap")
